Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-09-21 Review/3.workflow_cnb.tex
start

\subsection{Case 1: Scipion at CNB}
The National Center for Biotechnology (CNB) forms part of the Spanish National Research Council (CSIC), the largest public research institution in Spain. 
The CNB Cryo-Electron Microscopy Facility is a joint effort of the Nacional Center for Biotechnology (CNB-CSIC) and the Biological Research Centers (CIB-CSIC). The mission of the facility is to provide researchers access to the latest cryo-EM technology for high resolution imaging.

@@

At the beginning CNB networking setup was a quite straightforward one, movies were stored in the  same machine that ran \scipion and processed data were saved to external USB hard disks by this same machine. The situation changed when the new Falcon-III detector was installed. After that, data were produced at sustained speeds as high as 90 MB/sec (when acquiring four movies by hole in linear mode) and the main problem became to move smoothly the data through the entire pipeline from the microscope to the final user laboratory. In the following we describe such a pipeline.

From a network point of view there are three different levels of accessibility: (1) a private network that cannot be accessed by regular users, (2) the CNB LAN (local area network)  that can be accessed by any user which works inside the hosting  institution and (3) finally, there is a single computer that may be accessed from outside the institution and therefore, it can see the WAN (wide area network).

@@

The data flow is as follows: (a) the microscope system stores movies in the microscope-NAS, (b) when executing alignment-movie protocols \scipionbox reads the movies from the microscope-NAS but does not store them locally, (c) each hour, output-NAS connects to \scipionbox and copies -or updates- the last \scipion project, (d) at the same time output-NAS may be either executing a script to incrementally backup \scipion project and the movies to a USB disk or serve this information through the Internet and, (e) in parallel, \scipionbox transfers to  output-NAS different HTML reports that may be checked by users or staff with a HTML browser (see \url{http://nolan.cnb.csic.es/scipionbox/lastHTMLReport/}).

>>>>

\subsection{Case 1: Scipion at CNB}
The National Center for Biotechnology (\cnb) forms part of the Spanish National Research Council (CSIC), the largest public research institution in Spain. 
The \cnb Cryo-Electron Microscopy Facility is a joint effort of the Nacional Center for Biotechnology and the Biological Research Centers. The mission of the facility is to provide researchers access to the latest cryo-EM technology for high resolution imaging.

@@

At the beginning \cnb networking setup was a quite straightforward one, movies were stored in the same machine that ran \scipion and processed data were saved to external USB hard disks by this same machine. The situation changed when the new Falcon-III detector was installed. After that, data were produced at sustained speeds as high as 90 MB/sec (when acquiring four movies by hole in linear mode) and the main problem became to move smoothly the data through the entire pipeline from the microscope to the final user laboratory. In the following we describe such a pipeline.

From a network point of view there are three different levels of accessibility (see  \ffigure{fig:cnbpipeline}): (1) a private network that cannot be accessed by regular users -green lines in \ffigure{fig:cnbpipeline}-, (2) the \cnb LAN (local area network)  that can be accessed by any user which works inside the hosting  institution -blue lines in \ffigure{fig:cnbpipeline}- and (3) finally, there are two computers that may be accessed from outside the institution -red lines in \ffigure{fig:cnbpipeline}-, these computers give access to data and a web site respectively. s

\begin{figure}
  \centering
      \includegraphics[width=0.75\textwidth]{images/diagram.pdf}
  \caption{Graphical representation of the data flow through the CNB facility. Green, blue and red lines represent the microscope private network, the \cnb local area network and the public network respectively}
  \label{fig:cnbpipeline}

\end{figure}

@@

The data flow is as follows: (a) the microscope system stores movies in the microscope-NAS, (b) when executing alignment-movie protocols \scipionbox reads the movies from the microscope-NAS but does not store them locally, (c) output-NAS has access to Microscope-NAS and \scipionbox hard disks (d) output-NAS has a collection of scripts than may be used to incrementally backup \scipion project and the movies to a local or remote disk, or serve this information through the Internet and, (e) in parallel, periodically \scipionbox transfers to  HTML Server reports that may be checked by users or staff with a HTML browser (see \url{http://nolan.cnb.csic.es/scipionbox/lastHTMLReport/}).
